Balsa: A Compact Line Notation Based on SMILES

### 2022-07-02 manuscript.tex
Adds figures for atom parity and atom parity w/ suppressed hydrogen. Closes #14, closes #15.

The configuration about an atom can specified through its \ttt{parity} attribute. This attribute, together with a general convention, determine the relative three-dimensional positioning of substituents about a central atom. First, the parent of the central atom is identified. Then the frame of reference is shifted by sighting down the bond from the central atom's parent to the central atom. An equilateral triangle is then inscribed about the central atom. The bonds from the central atom are then iterated in order. If the parity of the central atom equals \ttt{Clockwise}, the child atoms attached through each bond are placed around the triangle in clockwise order. Otherwise the children are arranged in counterclockwise order.

\begin{figure}
    \centering
    \includegraphics{filler}
    \caption{Configurational descriptor. Configuration is either encoded or reconstructed using the same model.}
    \label{fig:configurational-descriptor}
\end{figure}

The procedure is modified for atoms bearing one virtual hydrogen and three atomic substituents. The implied bond to the virtual hydrogen is considered to precede the others. Sighting down this bond, the central atom's parent is placed on the triangle at an arbitrary position. Children are then iterated counterclockwise or clockwise relative to it.

\begin{figure}
    \centering
    \includegraphics{filler}
    \caption{Configurational descriptor with one virtual hydrogen. In this case, hydrogen assumes the role of the first substituent.}
    \label{fig:configurational-descriptor-vh}
\end{figure}

>>>>

The configuration about an atom can specified through its \ttt{parity} attribute. This attribute, together with a general convention, determine the relative three-dimensional positioning of substituents about a central atom (Figure~\ref{fig:atom-parity}). First, the parent of the central atom is identified. Then the frame of reference is shifted by sighting down the bond from the central atom's parent to the central atom. An equilateral triangle is then inscribed about the central atom. The bonds from the central atom are then iterated in order. If the parity of the central atom equals \ttt{Clockwise}, the child atoms attached through each bond are placed around the triangle in clockwise order. Otherwise the children are arranged in counterclockwise order.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{atom-parity.pdf}
    \caption{Atom parity. Four substituents surround a central atom with non-default atom parity (cyan). Sighting from the parent to the central atom, its children (a, b, and c) follow either a clockwise or counterclockwise pattern when iterated in order.}
    \label{fig:atom-parity}
\end{figure}

The convention is modified for atoms bearing one virtual hydrogen and three atomic substituents (Figure~\ref{fig:atom-parity-suppressed-hydrogen}). The implied bond to the virtual hydrogen is considered to precede the others. Sighting down this bond, the central atom's parent is placed on the triangle at an arbitrary position. Children are then iterated counterclockwise or clockwise relative to it.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{atom-parity-suppressed-hydrogen.pdf}
    \caption{Atom parity with one suppressed hydrogen. The central atom (cyan) has a suppressed hydrogen. In this case, the root atom (r) is regarded as the first child and analysis continues as before.}
    \label{fig:atom-parity-suppressed-hydrogen}
\end{figure}
